### 2020-02-01 paper/sex_selection_spacing-ver3.tex
Drop 4th spell for mortality because too few obs
Rewrite mortality section

% Revamped version for Demography focusing on method

@@

@@

[From conceptual framework section]
If short spacing lowers the survival probability of the next child, it is not, however, 
apparent that we should expect shorter spacing in the absence of boys.
There are two potential reasons why parents might still try to conceive sooner 
in the absence of boys.
One possibility is that parents do not realize that short spacing is potentially
detrimental to the next child's health, resulting in high mortality for both boys 
and girls born after short spacing across all households.

The other possibility is that parents realize that short spacing has adverse 
health effects, but their preference for sons is so strong that they are willing to 
divert substantial resources to the next child if it is a boy.
Assuming that these investments can compensate for the adverse effects,
we should see significant differences in mortality across sex for short-spacing 
children in the absence of boys.
If a son is born, his mortality risk should be substantially lower than expected 
for the spacing duration, and we should expect worse outcomes for the other 
children (all girls).
If a girl is born, there are two possible outcomes.
If parents treat all children/girls the same, we should see a slight worsening in 
health outcomes because fewer resources are available per child; 
if they do not, the last girl will have a much lower likelihood of surviving 
because the parents' incentive is to invest in their prior children rather than 
the new child.

With the adverse effects of shorter spacing strongly mitigated by higher education,
better-educated women can, in theory, have shorter spacing in the absence of a boy 
without substantial increasing mortality risk.
Differences in mortality outcomes across boys and girls are still possible,
but should not be as large as for less-educated women.
[end fro conceptual framework section]

The prior literature show that shorter birth spacing, especially very short spacing,
is associated with higher risk of infant mortality.
Hence, it is possible that the increasing use of sex-selective abortions could
directly reduce infant mortality by lengthening the duration from the prior birth.

There are a number of potential issues with understanding to what extent this
has happened.

First, the sex of the next child is no longer random, and boys, in the absence of
differential treatment, have higher infant mortality than girls.

Second, it may be that what matters is not the time between births, but rather 
between pregnancies, in which case multiple abortions followed quickly by new 
pregnancies would lead to shorter real spells of recovery.
The implication is that long spells might have a higher mortality risk since
they are now more likely with multiple abortions.

Third, as I show above the use of sex selection is more prevalent the higher the
education level of the mother.
Higher maternal education is, however, also associated with lower mortality risk
to begin with.
On top of this, with economic growth and better health care, infant mortality
may have fallen across all education groups and areas in the period covered.

I address three questions.

First, does the increased use of sex selection lead to higher mortality risk?

Second, has the negative effects of short spacing changed over time?

Third, how do the effects of short spacing vary by education level in India?

There are a number of problems with estimating the relationship between 
sex-selective abortions and infant mortality.

First, there are potential selection problem.
For example, women who face higher mortality risk of their children might forego 
the use of sex selection to ensure that they reach their desired number of 
children.
If these women also know to avoid very short birth spacing, the precense of 
these women in the sample would inflate the mortality of the "middle" birth
spacing, relative to the very short or very long birth spacing.

[our JDE paper]

An additional selection with the opposite effect is that women who have
difficulties conceiving or carrying a preganancy to term may also have higher 
mortality risk for their offspring, leading to a supriuos correlation
between very long birth spacing and mortality \citep{Kozuki2013}. 
If better health care and higher income means that more of these women are
now able to carry their pregnancy to term we can end up with more births
after long spells that have higher mortality risk but not because of the
increased use of sex selection.

[Our Demography paper shows a different type of selection effect, where the
use of sex selection biases the effect estimates of other variables that
vary together with the use of sex selection.]

Given the data and that the focus of this paper is mainly on the birth
spacing, a more in-depth treatment of these issue is the topic of future work.
Part of the problem here is also that the method used previously, such
as family fixed effects does not work well when the number of births is
very low as it is for higher education women who use sex 
selection, especially since the spacing from marriage to first birth
does not provide any information \citep{Kozuki2013,Molitoris2019}.
However, the fixed effects results and linear probability do not deviate
substantially.

Second, the actual number of abortions are unobserved.
The results above do show, however, how the use of sex selection vary
by education and sex composition of prior children.
I, therefore, estimate infant mortality risk taking into account the
sex composition of the prior children, as well as the index child.

Starting with the sample used for estimating birth spacing, I select, by
parity, children born more than 12 months before the survey month.
The dependent variable is whether the child died within the first twelve
months of life (infant mortality).
As above, I restrict the analysis to parity two through four.

The main set of explanatory variable consists of dummies for birth spacing,
divided into less than 15 months from when conception could realistically
could happen (same definition as above) and based on the finding that 
spacing less than 24 months between birth is associated with higher
infant mortality \citep{Molitoris2019}, and then in 12 months intervals
until TK, where all births after and until 96 months are included.%
\footnote{
\citet{Molitoris2019} has used quartic functions, but the concern is
that with the relatively small number sample here the shape
of the function would be strongly influenced by a small number of
observations.
Using dummies provides a more flexible specification and the standard
error will directly reflect the higher degree of noise for the
spells periods with fewer observations.
}
In addition, I use dummies for sex of the index child (the child whose 
mortality is estimated) and the sex composition of the prior children.
Birth spacing dummies, sex of index child, and sex composition dummies
are all interacted.
The other explanatory variables are the same as above and estimations
are done separately by education level.

I estimate probability of infant mortality using a logit model.
Results are presented as the predicted probability of dying within the
first year at the possible combinations of index child sex, sex composition
of prior children, and the birth spacing dummied.
All other variables are set to their average values.
[TK ehh, did I also do urban/rural?]

Figures \ref{fig:mortality_low} to \ref{fig:mortality_highest} show the 
estimated probabilities.
To ease legibility all confidence intervals are suppressed
(graphs with confidence intervals are available on request).

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{1972-1984}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p1_low_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p1_low_dummies} 
    \end{minipage}
}
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p1_low_dummies}
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{1985-1994}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p2_low_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p2_low_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p2_low_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{1995-2004}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p3_low_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p3_low_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p3_low_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{2005-2016}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p4_low_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p4_low_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p4_low_dummies} 
    \end{minipage}
} 
\caption{Predicted Probability of Infant Mortality for women with no education}
\label{fig:mortality_low}
\end{figure}

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{1972-1984}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p1_med_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p1_med_dummies} 
    \end{minipage}
}
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p1_med_dummies}
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{1985-1994}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p2_med_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p2_med_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p2_med_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{1995-2004}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p3_med_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p3_med_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p3_med_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{2005-2016}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p4_med_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p4_med_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p4_med_dummies} 
    \end{minipage}
} 
\caption{Predicted Probability of Infant Mortality for women with one to
seven years of education}
\label{fig:mortality_med}
\end{figure}

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{1972-1984}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p1_high_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p1_high_dummies} 
    \end{minipage}
}
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p1_high_dummies}
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{1985-1994}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p2_high_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p2_high_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p2_high_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{1995-2004}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p3_high_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p3_high_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p3_high_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{2005-2016}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p4_high_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p4_high_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p4_high_dummies} 
    \end{minipage}
} 
\caption{Predicted Probability of Infant Mortality for women with eight
to eleven years of education}
\label{fig:mortality_high}
\end{figure}

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{1985-1994}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p2_highest_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p2_highest_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p2_highest_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{1995-2004}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p3_highest_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p3_highest_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p3_highest_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{2005-2016}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p4_highest_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p4_highest_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p4_highest_dummies} 
    \end{minipage}
} 
\caption{Predicted Probability of Infant Mortality for women with twelve or
more years of education}
\label{fig:mortality_highest}
\end{figure}

For women with twelve or more years of education the results become very noisy
because of the low number of births, especially for parity three and four, and
the low mortality rate.
As above, I do not show results for the 1972--84 period because there were too
few women with this level of education for this period.

Based on the second parity births, women with twelve or more years of education
have the lowest infant mortality risk. 
Even for very short birth intervals the mortality risk is less than five percent,
and fall to less than half that for longer intervals.
Given the low mortality there is, not surprisingly, much difference between
the three periods covered.
Furthermore, there is no evidence that longer intervals are associated with
significantly higher mortality, especially for the groups most likely to have
used sex selection (women with a girl as their first child and a boy as their
second with a long interval).

Women with eight to eleven years of education have marginally higher mortality
risk than women with the most education, and also show slightly more evidence
of increased mortality with very short spacing.
Mortality risk have decreased slightly between periods, although the changes
are relatively minor.
As for women with the most education, there are not any statistically significant 
differences or increases in mortality with longer spacing.
Because of the low mortality risk and the relatively small number of births,
the estimates for the third and fourth parity are noisy.

Infant mortality risk for women with one to seven years of education have
clearly decreased over time.
This is also the first group that show increasing mortality risk with longer
spacing, although this effect mostly disappears for the later periods.
In other words, it does not appear to be the result of sex selection, but
rather arise from the selection bias discussed above where women with long
spells are those who find it difficult to either conceived and/or carry a 
pregnancy to term and also have higher mortality risk for their offspring.

Finally, women with no education have experienced substantial improvements
in infant mortality risk over time.
This decrease is especially pronounced for shorter intervals.
For the longer intervals, there is surprisingly little difference across
the education groups for the later periods.

@@

[TK things to cover:
- almost everybody marry, so these numbers should reflect cohort fertility relatively well
- what happens when women begin to join the labor force in larger numbers?
- better job oppportunities may be a direct way to affect sex selection since it makes 
it more expensive to have long spacing
- Incorporate Newman 1984 discussion (p 947) on income vs substitution effect
- why has fertility fallen at all? Lower mortality, higher quality children?
]

>>>>

@@

\usepackage{endfloat}`

@@

The prior literature show that shorter birth spacing, especially very short spacing,
is associated with higher risk of infant mortality.
Hence, the longer spacing, both from the increasing use of sex-selective abortions and
from secular changes, may directly reduce infant mortality.
To the extent that the longer birth intervals arise from multiple abortions
the short duration between \emph{pregnancies} could, however, increase mortality risk.

I address three questions.
First, how do the effects of short spacing vary by education level in India?
Second, has the negative effects of short spacing changed over time?
Finally, is the increased use of sex selection associated with higher mortality risk?

Starting with the sample used for estimating birth spacing, I select children born 
more than 12 months before the survey month.
I restrict the analyses to parities two and three because of the small number
of births and deaths for parity four.
Furthermore, I do not show results for women with twelve or more years of
education for the 1972--84 period because of the low number of women.

The dependent variable is whether the child died within the first twelve
months of life.
The main set of explanatory variable consists of dummies for birth spacing
covering 12 months intervals, starting from nine months after the prior birth 
as above, until 48 months, which includes all births until 96 months.
In addition, I use dummies for sex of the index child and the sex composition 
of the prior children.
The birth spacing dummies, the sex of index child, and the sex composition dummies
are all interacted.
Since the actual number of abortions are unobserved, the interactions between
sex composition of prior children and the sex of the index child serve
as proxies for the use of sex selection.
The other explanatory variables are the same as above and estimations
are done separately by education level and spell.

I estimate the probability of infant mortality using a logit model.
Figures \ref{fig:mortality_low} to \ref{fig:mortality_highest} present 
the predicted probability of dying within the first year at the possible 
combinations of index child sex, sex composition of prior children, and 
the birth spacing dummied.
All other variables are set to their average values.
To ease legibility all confidence intervals are suppressed
(graphs with confidence intervals are available on request).

An important caveat is that the estimations do not 
address potential selection problems.
For example, if women who have difficulties conceiving or carrying a pregnancy 
to term also have higher mortality risk for their offspring, the 
result may be a supriuos correlation between long birth spacing and 
mortality \citep{Kozuki2013}. 
Unfortunately, methods used previously to address selection, such
as family fixed effects do not work well when the number of births is
low as it is for higher education women \citep{Kozuki2013,Molitoris2019}.
On the positive side, the fixed effects results and linear probability in
prior research do not deviate substantially.

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{1972-1984}}
\subfloat[Second Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p1_low_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p1_low_dummies} 
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{1985-1994}}
\subfloat[Second Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p2_low_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p2_low_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{1995-2004}}
\subfloat[Second Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p3_low_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p3_low_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{2005-2016}}
\subfloat[Second Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p4_low_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p4_low_dummies} 
    \end{minipage}
} 
\caption{Predicted Probability of Infant Mortality for women with no education}
\label{fig:mortality_low}
\end{figure}

Women with no education have experienced substantial
improvements in infant mortality risk over time.
The decrease is especially pronounced for shorter
birth intervals.
The mortality risk for children with the shortest 
interval (the 0 to 11 months group, which is equivalent 
to 9 to 20 months after the prior birth) is
between 15 and 20 percent in the earlier periods, but
fall to less than 10 percent in the last period.

The mortality risk reductions for longer spells is
less pronounced, but still there.
For the latest period, the likelihood of dying within
the first year is below five percent.

Despite the prior findings of differential mortality
by sex, there is little evidence that girls have
substantially higher mortality risk, especially for
second births.
There is, however, some weak evidence that boys born
after two girls have slightly lower mortality risk,
although none of the differences are statistically
significant.

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{1972-1984}}
\subfloat[Second Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p1_med_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p1_med_dummies} 
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{1985-1994}}
\subfloat[Second Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p2_med_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p2_med_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{1995-2004}}
\subfloat[Second Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p3_med_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p3_med_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{2005-2016}}
\subfloat[Second Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p4_med_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p4_med_dummies} 
    \end{minipage}
} 
\caption{Predicted Probability of Infant Mortality for women with one to
seven years of education}
\label{fig:mortality_med}
\end{figure}

Infant mortality risk for women with one to seven years 
of education have also clearly decreased over time.
This is also the first group that show increasing 
mortality risk with longer spacing, although this effect 
disappears for the later periods.
In other words, it does not appear to be the result of 
sex selection, but rather arise from the selection bias 
discussed above.

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{1972-1984}}
\subfloat[Second Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p1_high_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p1_high_dummies} 
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{1985-1994}}
\subfloat[Second Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p2_high_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p2_high_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{1995-2004}}
\subfloat[Second Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p3_high_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p3_high_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{2005-2016}}
\subfloat[Second Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p4_high_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p4_high_dummies} 
    \end{minipage}
} 
\caption{Predicted Probability of Infant Mortality for women with eight
to eleven years of education}
\label{fig:mortality_high}
\end{figure}

For women with eight to eleven years of education, 
mortality risk have decreased slightly between periods,
although the changes are relatively minor.
The elevated mortality risk with very short spacing
is still evident, but the difference is much smaller 
than for the lower education groups.

If sex selective abortions lead to higher mortality
risk we should see an increase for longer spacing
when the child was a born and the prior children were
all girls (the solid lines).
There are no apparent differences between these groups
and the other potential combinations.
If anything, mortality risk for boys born after girls
have slightly lower mortality.
None of the differences are statistical signficant.

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{1985-1994}}
\subfloat[Second Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p2_highest_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p2_highest_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{1995-2004}}
\subfloat[Second Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p3_highest_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p3_highest_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{2005-2016}}
\subfloat[Second Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p4_highest_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.40\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p4_highest_dummies} 
    \end{minipage}
} 
\caption{Predicted Probability of Infant Mortality for women with twelve or
more years of education}
\label{fig:mortality_highest}
\end{figure}

Women with twelve or more years of education
have the lowest infant mortality risk based on the
second parity since the third parity results are very
noisy. 
Even for very short birth intervals the mortality risk is 
less than five percent,
and fall to less than half that for longer intervals.
Given the low mortality there is, not surprisingly, much 
difference between the three periods covered.
Furthermore, there is still no evidence that longer 
intervals are associated with significantly higher 
mortality, especially for the groups most likely to have
used sex selection (women with a girl as their first 
child and a boy as their second with a long interval).

Overall, the results show substantial convergence
in mortality risk across groups over time.
For the longer intervals, there is surprisingly little 
difference across the education groups for the later 
periods with even the no education group showing
an infant mortality risk of less than five percent.
Furthermore, with the adverse effects of shorter spacing 
strongly mitigated by higher education and no apparent 
increase in mortality risk from sex selection,
better-educated women can both try to conceive early
and and use multiple abortion in the absence of a boy
without substantial increasing mortality risk.

@@

[TK things to cover:
- almost everybody marry, so these numbers should reflect cohort fertility relatively well
- what happens when women begin to join the labor force in larger numbers?
- better job oppportunities may be a direct way to affect sex selection since it makes 
it more expensive to have long spacing
- Incorporate Newman 1984 discussion (p 947) on income vs substitution effect
- why has fertility fallen at all? Lower mortality, higher quality children?
- lower mortality and a higher than previously anticipated fertility implies that 
population growth in India is higher than expected.
]
